Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-19 papers/EMNLP2019/analysis.tex
pass over analysis section

In this section, we investigate to what extent names annotated in VisualGenome and elicited in ManyNames can be considered canonical, i.e. to what extent speakers agree in their naming choices.
Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on concept or category-level, we carry out an analysis on two different levels: First, we will look at instances and see to what extent names overlap for the same object. 
Second, we will use the existing annotation of names in VisualGenome to analyze agreement on the level of classes.
\begin{figure}[t]
	\centering
	\includegraphics[scale=.5]{figures/snodgrass_vanderwart_cake_042.png}
	\caption{Example of a picture of \textsl{cake} used in traditional picture naming studies \cite{snodgrass} \label{fig:picture_naming}}
\end{figure}

@@

Our analysis is based on the following annotations associated with each object: (i) the original name, annotated in VisualGenome, (ii) the object class or synset, annotated in VisualGenome and obtained via a semi-automatic linking of the object name to WordNet, (iii) the MN response set, i.e. a set of name types with annotation frequencies (max. 36 annotations per object). See Figure \ref{fig:ex} for examples of object annotations. Based on the VisualGenome synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.

As a first simple measure of variation in object naming, we simply count how many different names (i.e.\ types) are given to instances and to classes.
Since a certain amount of noise in the crowd-sourced MN data can be expected, we explore different frequency thresholds (from 1 to 6) to filter the response sets.
Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e. how many objects or classes have at least $n$ names.
Generally, without any frequency thresholding, the proportion of instances and classes that have a single name annotated is very small, i.e.\ below 10\% in both cases.

The histogram for instances in Figure \ref{fig:ntypes} suggests that there is a certain amount of low-frequency responses in the MN data which, again, is expected in an annotation task where subjects are free to choose any response that would like to. Thus, when filtering names with frequencies below 2, 3 or 4, the response sets for instances get more consistent such that the majority contains maximally 5 names.
Nevertheless, the proportion of objects that really only have a single name annotated is still below 50\%, even when applying a strict frequency filter of 4.
This indicates that there is non-negligible variation when different speakers name the same object, though the variation seems to be restricted to a manageable set of up to 5 names per object.

However, the number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure \ref{fig:ntypes} (right).
Here, we observe that the rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10 or even 20 different name types, even after applying the frequency thresholds. This clearly indicates that different instances annotated with the same name and synset in VisualGenome trigger different naming variants. Examples illustrating this can be found in Figure \ref{fig:ex}, where e.g. the response sets for different instances of the class \textit{bridge} have no overlap except for the name \textit{bridge}. Implications of this finding will be discussed below in Section \ref{subsec:discuss}.

@@

\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset), for filtered response sets (frequency threshold of 2)}
\label{tab:agree}
\end{table*}

@@

As type counts give a rather rough indication for variation in object naming, we analyse the following agreement measures which account for the distribution of names in the response sets:

\begin{itemize}
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
\item \textbf{$H$}: the $H$ agreement measure from \cite{snodgrass}, 0 is perfect agreement 
%\cs{How is this defined?}
\begin{equation}
H = \sum_{i=1}^k p_i\ log_2(1/p_i)
\end{equation}

@@

Again, we measure instance-level and class-level agreement on response sets for objects and classes respectively.
To account for potential noise, we filter the response sets for names with a frequency of 1 and use these to compute
the various measures shown in Table \ref{tab:agree}.
Generally, the agreement measures follow a similar pattern as the type counts discussed in \label{subsec:counts}:
On the instance-level, our annotators achieve a fair amount of overlap in their object naming choices, i.e. the dominant name is annotated by 75\% of the subjects and the original VisualGenome name has an average proportion of 62\% in the MN responses. On the class-level, however, the agreement is much lower, i.e.\ the average frequency of the dominant name drops to 56.4\% and the frequency of the VG name even more to 23.4\%. The $H$ measures indicates a fair amount of agreement for instances, which is a bit lower than the agreement found in picture norming studies on artificial images (e.g. \cite{snodgrass} report an average $H$ of 0.55). On the class-level, again, an average $H$ value of 2 points to a much more even distribution of name frequencies.

%Generally, this seems to suggest that indeed many objects in our data set have a canonical name. 
%\sz{For NLP people, this looks like a good agreement (given that people were free to type what they wanted). For vision people who might think of it as an object labeling task, this would be pretty low/bad agreement.}
%At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances. 
Furthermore, Table \ref{tab:agree} reports the agreement measures compute separately for the different domains in the MN data.
Two domains are particularly noteworthy: the \textsc{animals,plants} domain, which is often discussed in the object naming literature and where we find almost perfect agreement (with an $H$ value of 0.2), and the \textsc{people} domain with a particular low agreement.
For the other domains the $H$ value ranges around 1, and \%top is between 70\% and 80\%.
Another important aspect however is the large standard deviation values for both \%top and $H$, that we find both when averaging over all objects and within objects of the same domain. This indicates that the agreement measures are unstable for different instances and classes.
The qualitative examples in Figure \ref{fig:ex} further corroborate this evidence: depending on the visual instance, the agreement can be very high or very low.
The following Section will attempt to shed further light on the potential sources of this variation in object naming that we observe here.

@@

Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing objects names of different levels of specificity.
 We now investigate to what extent the naming variation in the MN data set (see previous Section) can be attributed and explained with specificity. 
 Given that the VisualGenome names are already linked to WordNet, we compute the same linking for the additional MN names, and check whether the MN name stand in a hierarchical taxonomic relation to 
 the object name's synset in VisualGenome.
%%In this section, we take a closer look at the lexical variation we observe in our data set. 
%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
%The naming variants can be grouped according to their lexical relation, as follows:
%
%\begin{itemize}
%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
%\item \textbf{hyponymy}: e.g.\ man vs. person
%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
%\item \textbf{no relation}: e.g.\  desk vs. apple
%\end{itemize}

Table \ref{tab:rel} shows how frequently names with a certain relation to the synset occur in the aggregated class-level response set, in terms of their  type and token frequency. 
Luckily, the coverage of WordNet for our name data is satisfactory, i.e. we were able to analyze 90\% of the name types which account for 97\% of the annotation tokens.
Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the VG annotators.
But overall, the most frequent case by far is that no hierarchical relation between the name and the synset can be retrieved from WordNet.
Thus, strikingly, most of the naming variation in MN is \textit{not} related to different preferences in levels of specificity, but to other sources.

\begin{table}
\small
\centering
\begin{tabular}{lcc}
\toprule
         relation & \% types & \% token \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 \\
\midrule
 synonym &  1.1 &  1.1 \\
 hyponym &  2.2 &  3.8 \\
 co-hyponym &  3.1 &  5.9 \\
 hypernym &  10.5 &  27.7 \\
 rel-not-covered &  72.2 &  58.3 \\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in MN to annotated VG synset, averaged over synsets}
\label{tab:rel}
\end{table}

Based on the examples in Figure \ref{fig:ex}, we will now provide a qualitative discussion of other types of variation we found in the data.

\begin{description}
\item[referential uncertainty:] despite our various attempts to filter objects that are occluded or have unclear bounding boxes \sz{see Section REF}, we still find many examples where annotators were uncertain about the identity of the object indicated by the bounding box and named an adjacent or a supporting object (e.g. \textit{bed-book}) or a part of the target object (\textit{batter-helmet})
\item[crossclassification:] a substantial group is constituted by names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-sandwich})
\item[conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (e.g. \textit{bed-bench},\textit{sandwich-hotdog})
\item[metonymy:] similar to crossclassification, we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (e.g.  \textit{sandwich-basket}, \textit{bed-bed sheet})
\item[issues with WordNet:] due to WordNet's fine-grained hierarchy, it can be difficult to retrieve certain loosely related synonyms or hypernyms (e.g. \textit{robe-dress})
\end{description}

As it is non-trivial to separate this cases in an automatic or manual manner, we leave a precise quantitative analysis of these phenomena for future work.

%\subsection{Qualitative Analysis}

%\sz{put qualititative discussion here} Table \ref{tab:qual} shows examples for canonical and non-canonical VG names in our data set, where canonical means that the name was the top response in the aggregated response set in ManyNames.

@@

 \caption{\label{fig:ex}Examples for different instances of VG synsets with low and high agreement in MN data set, names that have a hierarchical relation to the VG synset in WordNet are underlined}
\end{figure*}

@@

\subsection{Discussion (for now)}
\label{subsec:discuss}

Summarizing our analysis, we find that the object naming variation attested in our MN corpus offers some new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (psycho-)linguistics. 
Whereas existing large-scale collections of labels or names of objects in L\&V provide simple annotations of individual objects with canonicalized name sets, our data elicited from many speakers can be used to (i) assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to (ii) obtain available lexical alternatives of a preferred name, which again might vary strongly across instances and can often not simply be retrieved from existing taxonomies like e.g.\ WordNet. 
For theoretical research, our data offers a lot of variation in object naming that cannot be explained by adopting a traditional taxonomy-driven and hierarchical view.

So, \textit{do objects in real-world images have a canonical name?} As it turns out, this general question calls for a somewhat differentiated answer.
When taking other, similarly subtle and similarly free annotation tasks in NLP as a benchmark (e.g. \sz{????})
our analysis does indeed suggest that there are systematic properties of instances even in complex visual scenes that often make them have a dominant or strongly preferred name.
  At the same time, compared to annotation and modeling frameworks in Computer Vision that frame the problem as an object labeling task, our data shows a much lower agreement than what should be expected if object names were indeed entirely canonical, see e.g.\ the ResNet which achieves a top-1 error rate of 25\% on ILSVRC 2015.
Given that we find much lower agreement on object class-level than on instance-level, one might argue for using very fine-grained object annotations to remedy this problem. 
However, the fact that naming variants are often not recoverable by hierarchical relations suggest that even fine-grained recognition models cannot be expected to be able to simply infer recognition of more general classes (e.g., ILSVRC synset). Thus, neither simple multi-label classification nor more advance hierarchical approaches to object recognition seem to be well designed for capturing natural naming phenomena comprising crossclassification, metonymy and potentially other sources of variation.

>>>>

In this section, we investigate to what extent names in VisualGenome and ManyNames can be considered canonical, i.e., to what extent speakers agree in their naming choices.
Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on concept or category-level, we carry out an analysis on two different levels: First, we will look at instances and see to what extent names overlap for the same object. 
Second, we will use the existing annotation of names in VisualGenome to analyze agreement on the level of classes.
\begin{figure}[t]
	\centering
	\includegraphics[scale=.5]{figures/snodgrass_vanderwart_cake_042.png}
	\caption{Example of a picture of \textsl{cake} used in traditional picture naming studies \cite{snodgrass} \label{fig:picture_naming}}
\end{figure}

@@

Our analysis is based on the following annotations associated with each object: (i) the original name, annotated in VisualGenome, (ii) the object class or synset, annotated in VisualGenome and obtained via a semi-automatic linking of the object name to WordNet, (iii) the ManyNames response set, i.e. a set of name types with annotation frequencies (max. 36 annotations per object). See Figure \ref{fig:ex-high-low-agreement} for examples of object annotations. Based on the VisualGenome synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.

% As a first simple measure of variation in object naming, we simply count how many different names (i.e.\ types) are given to instances and to classes.
%Since a certain amount of noise in the crowd-sourced ManyNames data can be expected, we explore different frequency thresholds (from 1 to 6) to filter the response sets.
Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e. how many objects or classes have at least $n$ names, with different minimum frequency thresholds to account for possible noise in the crowdsourced data.
Without any frequency thresholding, the proportion of instances and classes that have a single name annotated is very small, below 10\% in both cases.

The histogram for instances in Figure \ref{fig:ntypes} suggests that there is a certain amount of low-frequency responses in the ManyNames data which, again, is expected in an annotation task where subjects are free to choose any response. When filtering names with frequencies below 2, 3 or 4, the response sets for instances get more consistent such that the majority contains maximally 5 names.
Nevertheless, the proportion of objects that really only have a single name annotated is still below 50\%, even when applying a strict frequency filter of 4.
This indicates that there is non-negligible variation when different speakers name the same object, and the variation seems to be restricted to a manageable set of up to 5 names per object.

However, the number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure \ref{fig:ntypes} (right).
Here, we observe that the rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10 or even 20 different name types, even after applying the frequency thresholds. This clearly indicates that different instances annotated with the same name and synset in VisualGenome trigger different naming variants. Examples illustrating this can be found in Figure \ref{fig:ex-high-low-agreement}. 
Implications of this finding will be discussed below in Section \ref{subsec:discuss}.

@@

\caption{Agreement in naming measured on the level of instances and on the level of \vgenome classes (i.e.\ after grouping objects by their \vgenome synset), for filtered response sets (frequency threshold of 2)}
\label{tab:agree}
\end{table*}

@@

%As type counts give a rather rough indication for variation in object naming, 
We compute the following measures to check agreement on the object names:

\begin{itemize}
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: $H = \sum_{i=1}^k p_i\ log_2(1/p_i)$

% \begin{equation}
% H = \sum_{i=1}^k p_i\ log_2(1/p_i)
% \end{equation}

@@

Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
To account for potential noise, we filter out names with a frequency of 1 from the response sets.
As shown in Table \ref{tab:agree}, generally, the agreement measures follow a similar pattern as the type counts discussed in the previous section:
On the instance level, our annotators achieve a fair amount of overlap in their object naming choices, with the most frequent name accounting for 75\% of the responses on average, and the original VisualGenome name having an average frequency of 62\% in the ManyNames responses. On the class level, however, the agreement is much lower: The average frequency of the top name drops to 56.4\% and the frequency of the \vgenome name even more, to 23.4\%. The $H$ measures indicates a fair amount of agreement for instances, a bit lower than the agreement found in picture norming studies on artificial images (e.g.\ \cite{snodgrass} report an average $H$ of 0.55). On the class-level, again, an average $H$ value of 2 points to a much more even distribution of name frequencies.

%Generally, this seems to suggest that indeed many objects in our data set have a canonical name. 
%\sz{For NLP people, this looks like a good agreement (given that people were free to type what they wanted). For vision people who might think of it as an object labeling task, this would be pretty low/bad agreement.}
%At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances. 
If we check agreement by domain, two domains stand out: the \textsc{animals,plants} domain, which is often discussed in the object naming literature and where we find almost perfect agreement (with an $H$ value of 0.2), and the \textsc{people} domain with a particularly low agreement.
In the other domains values are around the average for the whole dataset.
%For the other domains the $H$ value ranges around 1, and \%top is between 70\% and 80\%.
Another important aspect however is the large standard deviation values for both \%top and $H$, that we find both when averaging over all objects and within objects of the same domain. This indicates that the agreement varies a lot across instances, over and above the class or domain.
The qualitative examples in Figure \ref{fig:ex-high-low-agreement} further corroborate this evidence: depending on the visual instance, the agreement can be very high or very low.
These examples suggest that instances that are more prototypical of a category trigger higher agreeement.
The following Section will examine other potential sources of variation in object naming.

@@

Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing objects names of different levels of specificity~\cite{+++}.
This section shows that naming variation in ManyNames cannot be explained by this parameter.
Given that the VisualGenome names are already linked to WordNet, we compute the same linking for the additional ManyNames names, and check whether they stand in a taxonomic relation to the object synset given by VisualGenome.
%%In this section, we take a closer look at the lexical variation we observe in our data set. 
%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
%The naming variants can be grouped according to their lexical relation, as follows:
%
%\begin{itemize}
%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
%\item \textbf{hyponymy}: e.g.\ man vs. person
%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
%\item \textbf{no relation}: e.g.\  desk vs. apple
%\end{itemize}

Table \ref{tab:rel} shows the distribution of the results. 
how frequently names with a certain relation to the synset occur in the aggregated class-level response set, in terms of their  type and token frequency. 
\gbt{what do you mean, `` aggregated class-level response set''?}
The coverage of WordNet for our name data is satisfactory (90\% of the name types, accounting for 97\% of the tokens).
Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vgenome annotators.
However, in the vast majority of cases no hierarchical relation between the name and the synset can be retrieved from WordNet.
Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, but to other sources.

\begin{table}
\small
\centering
\begin{tabular}{lcc}
\toprule
         relation & \% types & \% token \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 \\
\midrule
 synonym &  1.1 &  1.1 \\
 hyponym &  2.2 &  3.8 \\
 co-hyponym &  3.1 &  5.9 \\
 hypernym &  10.5 &  27.7 \\
 rel-not-covered &  72.2 &  58.3 \\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vgenome synset, averaged over synsets.}
\label{tab:rel}
\end{table}

We provide a discussion of other types of variation we found in the data, based on qualitative analysis, and illustrating it with the examples in Figure \ref{fig:ex-high-low-agreement}:

\begin{description}
\item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box. They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}). Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
\item[Cross-classification:] a substantial group is constituted by names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
\item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench},\textit{sandwich-hotdog})
\item[Metonymy:] similar to crossclassification, we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}). 
\item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loosely related synonyms or hypernyms (\textit{robe-dress}).
\end{description}

As it is non-trivial to separate this cases, we leave a precise quantitative analysis of these phenomena for future work.

@@

 \caption{Examples for different instances of \vgenome synsets with low and high agreement in ManyNames data set, names that have a hierarchical relation to the \vgenome synset in WordNet are underlined}
\label{fig:ex-high-low-agreement}
\end{figure*}

@@

\subsection{Discussion}
\label{subsec:discuss}

% gbt: I moved the following sentence to the Conclusion section. To determine: what parts of this discussion stay here, what go to the conclusion.
% The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.

The answer to our question, \textit{do objects in real-world images have a canonical name?}, is nuanced.
Our data suggests that there is indeed a tendency for particular instances marked by bounding boxes to elicit a single consistent name across subjects, but there is also consistent variation in naming. Moreover, there is high variability in agreement across instances within the same class or domain.
The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation.

Existing large-scale collections of labels or names of objects in L\&V provide simple annotations of individual objects with canonicalized name sets.
When humans agree only around 70\% of the cases in how to name an object, it is not clear that the data can be taken as a gold standard in multi-label classification setting, as is commonly done in Computer Vision.
  % At the same time, compared to annotation and modeling frameworks in Computer Vision that frame the problem as an object labeling task, our data shows a much lower agreement than what should be expected if object names were indeed entirely canonical,
See e.g.\ the ResNet which achieves a top-1 error rate of 25\% on ILSVRC 2015. \gbt{It is not clear to me what this means: what kind of data is this? how does this result relate to our point? -- @Carina, expand?}
Our data can be used to (i) assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to (ii) obtain available lexical alternatives of a preferred name, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet. 
For theoretical research, we show that much of the variation in object naming cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature.

\gbt{I couldn't follow the discussion in the following pargraph. Do you think it's subsumed by the one above? Can we remove it?} 
Given that we find much lower agreement on object class-level than on an instance-level, one might argue for using very fine-grained object annotations to remedy this problem. 
However, the fact that naming variants are often not recoverable by hierarchical relations suggest that even fine-grained recognition models cannot be expected to be able to simply infer recognition of more general classes (e.g., ILSVRC synset). Thus, neither simple multi-label classification nor more advance hierarchical approaches to object recognition seem to be well designed for capturing natural naming phenomena comprising crossclassification, metonymy and potentially other sources of variation.
